A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise Abstract

\begin{abstract}
This paper serves as a survey on \textit{ordered binary Decision diagrams}
(\textit{OBDDs}). It provides an overview of the OBDD representation, the
operations which can be applied efficiently on OBDDs and some aspects when it
comes to implementing OBDD packages. Moreover, their limitations and their
application in symbolic model checking are outlined and alternative representations
are presented to tackle these limitations. As this is just a survery, no new
insights are provided whatsoever.
\end{abstract}

>>>>

\begin{abstract}
This paper serves as survey on \textit{ordered binary Decision diagrams}
(\textit{OBDDs}). It provides an overview of the OBDD representation, the
operations which can be applied efficiently on OBDDs and some aspects when it
comes to implementing OBDD packages. Moreover, their limitations and their
application in symbolic model checking are outlined and alternative representations
are presented to tackle these limitations. As this is only a survey, no new
insights are provided whatsoever.
\end{abstract}
